Title Goes Here

### 2020-02-24 paper/paper.tex
formatting
absEnv interp. of tail rec and lambdas (also fixed width formatting for lstlisting)

\lstset{language=haskell, deletekeywords={abs}}

@@

@@

absEnv env env (Var v) =
  case envLookup env v of
    Just x -> absEnv env
    Nothing ->
      error
        ("No binding for name "
          ++ show v)

@@

\subsection{Overall Control Flow of the Core Plugin}

>>>>

\lstset{language=haskell, deletekeywords={abs},basicstyle=\ttfamily}

@@

absEnv env (TailRec f) = \ x ->
  case absEnv env f x of
    Step x' -> absEnv env (TailRec f) x'
    Done r  -> r

absEnv env (Var v) =
  case envLookup env v of
    Just x -> absEnv env
    Nothing ->
      error
        ("No binding for name "
          ++ show v)

absEnv env (Lam (name :: Name a)
                (body :: E b)) =
  \ (arg :: a) ->
    let go :: forall x. E x -> E x
        go expr@(Var name2 :: E a') =
          case namesEq name name2 of
            Just Refl -> rep arg
            _ ->
              case envLookup env name2 of
                Just v  -> v
                Nothing -> expr

        -- [... traverse rest of expression
        --      in go ...]
    in
    absEnv (extendEnv env
                      (name :=> rep arg))
           (go body)

@@

@@

\clearpage
\subsection{Overall Control Flow of the Core Plugin}
